\section{List of hardware used} \label{app:hardwareused}

\begin{itemize}
	\item DSLR body (9 units in total): Canon EOS 700D
	\item Lens (one for each camera): Canon EF 50mm f/1.8 II
	\item Power adapter (one for each): Canon ACK-E8
	\item Memory card (one for each): Transcend SDHC class 10 UHS-I 16GB
	\item USB hub (3 units): D-link DUB-H4
	\item Remote board: custom built around ST Nucleo-F401RE, see next section \ref{app:remotetrigger}
	\item Stand (four units): Millenium LST-310, a sturdy three-legged lighting stand with a pole that can be zoomed several meters high.
	\item Ball head (one for each): Manfrotto 494
	\item Clamp (one for each): Manfrotto 035 Super Clamp, with Manfrotto 036-38 studs
	\item Velcro strap etc. for fastening things
\end{itemize}


\section{Remote trigger} \label{app:remotetrigger}

The remote trigger consists of a Nucleo-F401RE microcontroller platform by ST microelectronics, and supporting hardware for connecting the cameras.
Each camera connects to the trigger via a 2,5mm stereo plug, as the cameras have a standard 2,5mm jack for remote trigger.
To secure the cameras from each other, the remote wires are connected with opto-isolators (TLP621-2).

some pictures here.

\subsection{Schematic}


\subsection{Circuit board layout}

A complete PCB was not designed because of the simplicity of the system.
Instead, the parts were soldered on a piece of perfboard, a piece of PCB with pre-drilled regular grid of holes with copper pads.

pictures here too.

\subsection{Parts list}

\begin{itemize}
	\item ST Microelectronics Nucleo-F401RE microcontroller platform
	\item 10 x stereo 2,5 mm jack
	\item 10 x stereo 2,5mm male-male 3 meter cable
	\item 10 x TLP621-2 opto-isolator
	\item (usb cable, wire, buttons?)
\end{itemize}
