\section{Applications}

The application domain for reconstructing three-dimensional fields is wide, and expands constantly with the ever increasing computing power.
The popularity of handheld computers - smartphones - equipped with relatively good quality cameras is currently an attractive target for 3d scanning software, while the actual reconstruction works in the cloud.
Kinect, the active infrared-based scanner for the xbox console, has reached a phase where it can be considered ubiquitous in gaming.

The Matrix (1999) \cite{wachowski99matrix}, famous of the bullet-time scenes, used heavy optical flow processing to ``slow time down''; it is a good example on what is needed to capture data that changes over time in non-controllable and non-repeatable ways.
The Matrix Reloaded \cite{wachowski03reloaded} used a technique called Universal Capture by Borshukov et al.
\cite{borshukov05universal} to encode and simulate accurate facial movements in 3D.

Facial surface motion capture (mocap) is currently a standard tool in the movie and video game entertainment industry among the more mature mocap for whole body movement to record performances for replaying them later.
Mocap records movements of a human body or another object that is to be recorded so that the movements can be replayed or analyzed.
Recent movies and video games (such as \cite{rockstar2011noire}) have shown that by capturing real motion of facial expressions instead of simulating them produces impressive results.
Literature on capture of human faces and skin surface motions is large. \cite{deng2007computer}
Professional quality capture still needs a laboratory environment with a large number of cameras \cite{winder2008technical,motionscan}.

Human performance capture is traditionally done on special easily distinguishable markers, typically small retroreflective patterns, that are mapped to a model for playback. Playback then interpolates between the recorded positions. Advances in camera resolution make it possible to use only texture features without separate markers.
% http://www.siggraph.org/education/materials/HyperGraph/animation/character_animation/motion_capture/history1.htm

Cloth motion is another highly nonrigid application that can be scanned for acquisition of model parameters. \cite{pritchard2003cloth}

Large scale static 3D scanning and texturing of archeologic sceneries is done with combining laser scanning and photographs \cite{lerma2010terrestrial}.

Small objects have been scanned successfully with a turntable \cite{fitzgibbon1998automatic}, and structure from motion techniques have recently been presented that impressively recover a structure from pictures taken all over an outdoor location with no a priori information about the camera configurations. \cite{goesele2007multi,furukawa2010towards}.

Static applications are more developed; while dynamic scanning has lots of interest in scanning faces and human motion, also static cases have received attention in medical applications, landscape/architecture engineering and mapping, and crime scene investigation.
